\section{Introduction}

The interpretation of total-field anomalies on the surface of the Earth is an 
important challenge in exploration geophysics due to the nonuniqueness of 3-D magnetic 
inversion. It is well-known that several magnetization distributions in the subsurface 
can reproduce the same magnetic data with the same accuracy. 
To overcome this inherent ambiguity, a priori information needs to be introduced 
for reducing the number of possible solutions that are coherent with the local geology.
The available a priori information determines the suitable inversion method to be applied. 
As explained below, we identified, in the literature, three groups of 3-D magnetic inversion methods.

The first group of inverse methods approximates the source by a geometrically 
simple causative body having its geometry defined by a small number of parameters 
\cite[e.g., ][]{ballantyne-1980,bhattacharyya-1980,silva-1983,medeiros_silva1995}. These methods 
estimate both the geometry and the physical property of the source by solving 
a nonlinear inverse problem. Due to the very restrictive parametrization, 
such methods usually do not have severe problems with ambiguity.

The second group of inverse methods is formed by the vast majority of methods. 
These methods approximate the subsurface by a grid of juxtaposed rectangular prisms having 
a constant total-magnetization direction. Some methods presume a purely induced 
magnetization and the isotropic magnetic susceptibility of the prisms is the quantity estimated by solving a linear inverse problem. 
Some examples of this linear inversion are presented by \cite{cribb-1976}, \cite{li_3-d_1996} and \cite{pilkington_3-d_1997}.
Different approaches have improved this linear inversion to obtain focused images of the subsurface. 
For example, \cite{portniaguine_focusing_1999} and \cite{portniaguine_3d_2002} introduced the minimum gradient support functional, similar to the one proposed by
\cite{last-1983} that minimizes the volumes of the sources in a gravity data inversion. 
By inverting magnetic anomaly and any component of the total anomalous field, this functional estimates a magnetization distribution that generates a non blurry (focused) 3-D image of the geologic bodies in the subsurface.
\cite{barbosa_interactive_2006} presented a method for inverting interfering magnetic anomalies produced by multiple sources by combining features of the forward modeling (the interactivity) and traditional inversion (the automatic data fitting). Other studies introduced strategies to constraint the nonuniqueness and delineate the source \cite[]{tontini,pilkington_3d_2009,shamsipour_3d_2011,cella_inversion_2012,abedi-2015}. 
Some of these methods allowed remanent magnetization \cite[e.g., ][]{pignatelli-2006}. 
In this case, the parameters to be estimated are the total-magnetization intensities 
of the prisms. 
In all these methods, the geometries of the magnetic sources are indirectly retrieved by interpreting the estimated total-magnetization intensity 
distribution. 
Theoretically, these inversion methods are capable of recovering the geometry of complex 
sources. However, they require a plethora of a priori information to overcome 
their nonuniqueness and instability due to the large number of parameters 
to be estimated. Additionally, they are characterized by a high 
computational cost associated with the solution of large linear systems.

The third group of 3-D magnetic inversion methods requires some knowledge about the 
physical property distribution to estimate the geometry of the sources. 
They are usually formulated as nonlinear inverse problems. 
\cite{wang_inversion_1990} approximated the source by a polyhedron and estimate 
the position of its vertices in the Fourier domain. 
\cite{wenbin-2017} developed a multiple level-set method to estimate geometry 
of a set of causative bodies with uniform magnetic susceptibility. 
\cite{hidalgo-2019} inverted the total-field anomaly for estimating the depths to the top of a magnetic basement of a sedimentary basin with known magnetization intensity but unknown magnetization direction. 
An inverse method in this third group has a small number of parameters to be estimated by inversion and has much less ambiguity in comparison to the second group. 

By following the third group of 3-D magnetic inversion methods, 
we present a method to estimate the geometry, position and total-magnetization
intensity of an isolated and uniformly magnetized 3-D source with known
total-magnetization direction.
Our method is an extension of the methods presented 
by \cite{oliveirajr-etal2011} and \cite{oliveirajr-barbosa2013} for inverting, respectively, 
gravity and gravity-gradient data, applied to the total-field anomaly. 
We approximate the source by a stack of vertically juxtaposed 
right prisms with polygonal horizontal cross-sections and the same number of vertices.
All prisms have the same thickness and total-magnetization intensity.
Differently from \cite{oliveirajr-etal2011} and \cite{oliveirajr-barbosa2013}, 
our method estimates not only the horizontal Cartesian coordinates of the origins and the radii of the vertices describing the horizontal cross-sections of all prisms but also the thickness of all prisms comprising the interpretation model, as well as
two additional parameters: the depth to the top of the shallowest prism and the
total-magnetization intensity of all prisms. 
We perform a series of inversion runs using different value combinations of these two parameters and compute a goal function associated with each of the trial solutions.
Among the estimated models, those producing the 
lowest values of goal function form the set of candidate models.
To obtain stable solutions, we use the same set of regularizing functions proposed by 
\cite{oliveirajr-etal2011} and also propose a new one for constraining the 
thickness of the prisms. 
Following \cite{oliveirajr-etal2011} and \cite{oliveirajr-barbosa2013}, we refer to the proposed method as \textit{radial inversion} because our method estimates the radii of the vertices describing the horizontal cross-sections of all prisms.
Tests on synthetic data and on airborne magnetic data collected over the alkaline-carbonatitic complex of Anit{\'a}polis, in southern Brazil, show the potential of our method in retrieving 3-D magnetic bodies even if they exhibit a variety of shapes and depths. 


